DATA 621 Homework #2

### 2019-09-27 hw2/HW2.Rmd
Additional work on HW2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(caret)
library(pROC)
```

@@

cm <- confusion_matrix(df, actual, predicted)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(caret)
library(pROC)
# Thank you Stack Overflow!
# A Prefix nulling hook.

# Make sure to keep the default for normal processing.
default_output_hook <- knitr::knit_hooks$get("output")

# Output hooks handle normal R console output.
knitr::knit_hooks$set( output = function(x, options) {

  comment <- knitr::opts_current$get("comment")
  if( is.na(comment) ) comment <- ""
  can_null <- grepl( paste0( comment, "\\s*\\[\\d?\\]" ),
                     x, perl = TRUE)
  do_null <- isTRUE( knitr::opts_current$get("null_prefix") )
  if( can_null && do_null ) {
    # By default R print output aligns at the right brace.
    align_index <- regexpr( "\\]", x )[1] - 1
    # Two cases: start or newline
    re <- paste0( "^.{", align_index, "}\\]")
    rep <- comment
    x <- gsub( re, rep,  x )
    re <- paste0( "\\\n.{", align_index, "}\\]")
    rep <- paste0( "\n", comment )
    x <- gsub( re, rep,  x )
  }

  default_output_hook( x, options )

})
knitr::opts_template$set("kill_prefix"=list(comment=NA, null_prefix=TRUE))
```

## Confusion Matrix

@@

confusion_matrix(df, actual, predicted) %>%
  kable() %>%
  kable_styling()
```

## Accuracy

```{r, null_prefix=TRUE}
accuracy(df, actual, predicted)
```

## Classification Error Rate

```{r, null_prefix=TRUE}
classification_error_rate(df, actual, predicted)
```

### Verify Accuracy and Error Rate Sum to 1

```{r, null_prefix=TRUE}
accuracy(df, actual, predicted) + classification_error_rate(df, actual, predicted)
```

## Precision

```{r, null_prefix=TRUE}
precision(df, actual, predicted)
```

## Sensitivity

```{r, null_prefix=TRUE}
sensitivity(df, actual, predicted)
```

## Specificity

```{r, null_prefix=TRUE}
specificity(df, actual, predicted)
```

## F1 Score

```{r, null_prefix=TRUE}
f1_score(df, actual, predicted)
```
### F1 Score Will Always be Between 0 and 1
